Constructing the transition graphs of interacting hysterons

### 2022-07-01 Paper_draft.tex
Minor changes: 'the same' -> 'equivalent when comparing graphs, removed reference to hysterons as 'indistinguishable'
Changed 'we have shown that it is straightforward to construct all Preisach graphs' to 'there is a one-to-one relationship' as we do not show the process; changed linear model in intro ordering to general

When we define the state $S = \{s_1, s_2, ..., s_N\}$, the labelling of hysterons 1 through N is arbitrary. As a result, when two graphs only differ from one another by the ordering of the hysterons 1, 2, ..., N, we consider the graphs to be the same (Fig. \ref{fig:exchangeplusgoe}a).\\

@@

We now describe how the transition graph is constructed for a given set of bare switching fields $\{u_i^{+, -}\}$ and coupling coefficients $c_{ij}$.\\

@@

We have shown that it is straightforward to construct all Preisach graphs by considering all permutations of the down switching fields. When hysterons are allowed to interact, however, the situation changes. On one hand, there are then $2(2^N-1)$ states $U_i^{+, -}(S)$, and because of the possibility of avalanches, the ordering between all of the states must be considered. On the other hand, the state transition graph is only determined by a partial order between some of the switching fields. As a result, the number of permutations $(2(2^N-1))!$  for interacting hysterons greatly outnumbers the number of unique state transition graphs. For $N=2$, the number of permutations is $8! = 40320$ while we know the number of graphs to be only 13. For $N=3$, the number of permutations is as high as $24! \approx 6\times 10^{23}$.\\

>>>>

When we define the state $S = \{s_1, s_2, ..., s_N\}$, the labelling of hysterons 1 through N is arbitrary. As a result, when two graphs only differ from one another by the ordering of the hysterons 1, 2, ..., N, we consider the graphs to be equivalent (Fig. \ref{fig:exchangeplusgoe}a).\\

@@

We now describe how the transition graph is constructed for a given set of switching fields $U_i^{+, -}(S)$.\\

@@

We see that for the Preisach model, there is a one-to-one relationship between the permutations in the orderings of the switching fields $u_i^{+, -}$ and the possible transition graphs. When hysterons are allowed to interact, however, the situation changes. On one hand, there are then $2(2^N-1)$ states $U_i^{+, -}(S)$, and because of the possibility of avalanches, the ordering between all of the states must be considered. On the other hand, the state transition graph is only determined by a partial order between some of the switching fields. As a result, the number of permutations of the switching fields $(2(2^N-1))!$  for interacting hysterons greatly outnumbers the number of unique state transition graphs. For $N=2$, the number of permutations is $8! = 40320$ while we know the number of graphs to be only 13. For $N=3$, the number of permutations is as high as $24! \approx 6\times 10^{23}$.\\
